Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-16 paper.tex
minor changes
chore: fix time

Let $\Gamma$ be the aggregate program that takes a graph $G_t$ decorated by $o^t_v$, 

@@

 $f_v = (\theta^v_t, o^t_v)$. \lukas{we used $o_v$ to describe the observation of node $v$ in section II.C - so this would not include field information, right?}

@@

 producing an action $a_t$ that will then modify the global state of the system.

>>>>

Let $\Gamma$ be the aggregate program that takes a graph $G_t$ decorated by $o^v_t$, 

@@

 $f_v = (\theta^v_t, o^v_t)$. \lukas{we used $o_v$ to describe the observation of node $v$ in section II.C - so this would not include field information, right?}

@@

 producing an action $a^v_t$ that will then modify the global state of the system.
